A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-11 doc/draft-01-stokes/03analysis.tex
cleaning up paper and adding annulus discretization plot

Before proving the main theorems, we require a number
of uniqueness results for oscillatory Stokes boundary
value problems.
%
To prove the uniqueness results, we follow the 
structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
for the scalar Helmholtz equation.
While uniqueness results for interior Dirchilet, Neumann, and impedance
problems follow from energy considerations and compactness
arguments, the proofs for uniqueness of exterior
results are more involved. 
In particular,
this entails making the exterior problems
well-posed by imposing an appropriate radiaiton condition.
We present well-posed boundary value formulations 
for both interior and exterior Dirichlet, Neumann and impedance
boundary value problems, and also
present uniqueness results for all of them.

@@

Let $\Omega$ be a bounded domain with $C^2$ boundary
denoted by $\Gamma$.
The Dirichlet problem specifies the
velocity of the fluid on the boundary, i.e.

\begin{definition}[Interior Dirichlet problem]
  Let $\ff \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:dir_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bu &= \ff \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}
Note that the divergence-free constraint for the oscillatory
Stokes equations implies a compatibility condition on the
Dirichlet data $\ff$, namely that
\begin{equation} \label{eq:dir_compat}
  \int_\Gamma \ff \cdot \bnu \, dS = 0 \; .
\end{equation}

Let $\bsigma$ denote the stress tensor associated with
field $(\bu,p)$. 
Specifying the surface traction, $\bt = \bsigma \cdot \bnu$,
on the boundary gives the Neumann boundary value
problem, i.e.

\begin{definition}[Interior Neumann problem]
  Let $\bg \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt &= \bg \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

\begin{definition}[Interior impedance problem]
  Let $\bh \in C(\Omega)$ be given and suppose 
  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)}>0$. 
  Find $(\bu,p) \in A(\Omega)$  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt - i \eta \bu &= \bh \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

@@

\begin{equation}
\left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
- ik \left(\nabla^\perp \otimes \nabla^\perp
\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | =
o ( 1/\sqrt{r} ) \; . \nonumber
\end{equation}
Finally, because $H_0^{(1)}(kr)$ is radially symmetric,
we have

@@

Let $E$ and $\Gamma$ be as in the previous subsection.
The radiation condition allows for a well-posed formulation
of the exterior boundary value problems, which we
summarize in
\cref{def:dir_exterior,def:neu_exterior} below.

@@

\begin{definition}[Exterior Impedence problem]
  \label{def:neu_exterior}  
  Let $\bh \in C(\Gamma)$ be given and suppose that
  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)} >0$. 
  Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt + i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

@@

In the following lemma, we prove uniqueness for the
interior impedence problem.

@@

The following lemmas are useful in establishing the uniqueness
of oscillatory Stokes boundary value problems.

@@

In the next lemma, we prove the analogue of Rellich's lemma for the
oscillatory Stokes equation. 
\begin{lem}
  \label{lem:rellich}
  Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose $k$ is real, $\bu$ satisfies the oscillatory
  Stokes equation in $E$, and that 
\begin{equation}
\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
\, . \label{eq:decayatinf}
\end{equation}
Then each component of $\bu$ is harmonic in $E$.
\end{lem}
\begin{proof}
We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
oscillatory biharmonic equation in $E$, i.e.
\begin{equation}
\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
\end{equation}
For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
j=1,2 \, . \nonumber
\end{equation}
Using Parseval's identity then
\begin{equation}
\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
|a_{2,n}(r)|^2 \, . \nonumber
\end{equation}
Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
\begin{equation}
\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
\end{equation}
Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
the functions $a_{j,n}$ are linear combinations of 
\begin{equation}
r^{|n|}, r^{-|n|}, H^{(1)}_{n}(k r), H^{(2)}_{n}(k r) \, , \quad
n\neq 0 \, , \nonumber
\end{equation}
and
\begin{equation}
1, \log{(r)}, H^{(1)}_{0}(k r), H^{(2)}_{0}(k r) \quad n=0 \, ,  \nonumber
\end{equation} 
where $H_{n}^{(1),(2)}(\cdot)$ are the Hankel functions of the first and
second kind of order $n$.
Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
expansion of $H_{n}^{(1),(2)}(kr)$ when $k$ and $r$ are real-valued, we note
that the projection of $a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$
must be zero. Thus, 
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
\, , \nonumber
\end{equation}
for sufficiently large $r$.
Finally, by \cref{cor:analytic}, $\bu$ is
analytic in $E$. Therefore, each $u_j$ is harmonic
throughout $E$.
\end{proof}

@@

\begin{remark}
  It should be noted that in~\cref{lem:rellich}, $\bu$ need
  not be a radiating solution. All that is assumed of $\bu$
  is that it satisfies the PDE in $E$.
\end{remark}

@@

The rank deficiency of $\cI-2\cDk$ is
well-known~\cite{biros2002embedded} and we summarize it
in

\begin{lem}[\cite{biros2002embedded}]
  \label{lem:nunull} In the notation above,
  $\bnu \in \cN(\cI - 2\cDkt)$.
\end{lem}
\begin{proof}
From~\cref{lem:propnullspacecorr}, we note that
$W[(\cI - 2\cD_{k})\bmu] =0$ implies that
$\left<(\cI -2\cD_{k})\bmu ,\bnu \right> = 0$ for
all $\bmu$, i.e. $\bnu \in R(\cI - 2\cD_{k})^{\perp}$, where
$R(A)$ denotes the range of the operator $A$. 
By the Fredholm alternative, the result then follows.
\end{proof}
Thus, we instead analyze the equation
\begin{equation}
(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
\end{equation}
Note that if $\ff$ satisfies the compatibility
condition $\int_\Gamma \ff \cdot \bnu \, dS =0$, then
\cref{eq:inteq_dir_int_mod} implies \cref{eq:inteq_dir_int}.

@@

\begin{thrm}
\label{thm:dlmain}
Suppose that $\Omega$ is a bounded, simply connected domain. Then, the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k^2$ is a
Dirichlet eigenvalue for the Stokes equation on $\Omega$.
\end{thrm}
\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for
  the Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-}$, is given by $(\cI - 2\cD_{k}) \bmu = 0$
on $\Gamma$. Since $k^2$ is not a Dirichlet eigenvalue for the Stokes
equation on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
In particular, this implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again, we conclude that the exterior limit
of the surface traction, $\bt^{+}$, is $0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Stokes equation in the exterior $E$, as $\cW[\bmu] = 0$ implies
$\int_{\Gamma} \bmu \cdot \bnu = 0$.
From the uniqueness of the Neumann problem in the
exterior $E$, we conclude that $\bu \equiv 0$ in $E$ as well,
which in particular implies that
the exterior limit of the velocity, $\bu^{+}$, is $0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $2\bmu = \bu^{-} - \bu^{+} = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.

@@

\begin{thrm}
  Suppose that $\Omega$ is a multiply connected domain
  given by the intersection of a domain $\Omega_{0}$
  and the exterior of a single domain $\Omega_{1}$ with
  $ \bar\Omega_1 \subset \Omega_0$.
  Then, the operator $\cI - 2\cD_{k} - 2\cW$ has a non-trivial
  null space if $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
\end{thrm}

@@

\begin{proof}
  Suppose that $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
  Let $\tilde{\bu}$ be the eigenfunction corresponding to $k^2$. 
  Note that $\tilde{\bu}$ is not identically $0$ on the boundary
  of $\Omega_{1}$, which we denote by $\Gamma_1$.
  Since $\tilde{\bu}$ is an interior Neumann eigenfunction, we note that
  the surface traction corresponding to the solution, $\bt^{-}$, is $0$
  on the boundary.
  Applying \cref{thrm:rep-theorem} to the
  solution $\tilde{\bu}$ in the interior
  and taking the interior limit we get
\begin{equation}
\tilde{\bu} = \frac{1}{2}\tilde{\bu} + \cD^{\Gamma_{1}}_{k}[\tilde{\bu}] +
\cS^{\Gamma_{1}} [\bt^{-}] \implies \frac{1}{2} \tilde{\bu} - \cD^{\Gamma_{1}}_{k}[\tilde{\bu}]
= 0\, .
\end{equation}
Note that the sign of the $\bD$ operator in the
representation theorem is switched since the normal
is pointing inwards for the boundary $\Omega_{1}$.
Thus, $\tilde{\bu}$ is a non-trivial null vector of the operator 
$\frac{1}{2}\cI - \cD^{\Gamma_{1}}_{k}$. 
Furthermore since $\tilde{\bu}$ is the boundary data of 
the solution of the oscillatory Stokes equation
in $\Omega_{1}$, we get that $\cW^{\Gamma_{1}}[\tilde{\bu}] = 0$.
Setting $\bmu = \tilde{\bu}$ on $\Gamma_{1}$, and
$\bmu = 0$ on $\Gamma_{0}$, we obtain a non-trivial null
vector for the operator $\cI - 2\cD^{\Gamma}_{k} -2\cW^{\Gamma}$
on the boundary $\Gamma = \Gamma_{0} \cup \Gamma_{1}$.
\end{proof}

The spurious eigenvalues of the operator $\cI-2\cDk-2\cW$
are demonstrated in \cref{subsec:spurannulus} on an annulus,
where both the true and spurious eigenvalues can be
determined analytically. 
Analogous with the observation in~\cite{zhao2015robust},
this lack of one-to-one correspondence between
the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
and the Dirichlet eigenvalues of the Stokes operator on multiply
connected domains also causes non-robustness and introduces near 
resonances for simply connected domains
which are almost multiply connected.
We demonstrate this issue numerically
in~\cref{subsec:crescent}.

@@

The non-robustness in using the double layer
potential representation observed above can be
remedied by using a combined-field, or mixed layer potential,
representation, i.e. setting $\bu = (\bD_{k} + i\eta \bS_{k})
\bmu$, with $\eta$ real and positive.
Imposing the Dirichlet boundary condition
and using~\cref{lem:jump-conds}, we obtain 
\begin{equation}
  (\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \,
  \textrm{ on } \Gamma. 
\end{equation}
As with the double layer representation, this
integral equation is rank deficient for any $k$.
Instead, we consider
\begin{equation}
(\cI - 2\cD_{k} -2i\eta \cS_{k}  -2\cW)\bmu = -2 \ff \, .
\end{equation}

@@

To show that $\bmu=0$ on
$\Gamma_{j}$, we observe that $\bu$ is also a
solution to the oscillatory Stokes equation in each
of the obstacles $\Omega_{j}$.
Using the jump conditions in~\cref{lem:jump-conds},
we get that $\bt^{+} = 2i\eta \bmu$ and $\bu^{+} = -2\bmu$.
However, the normal is inward pointing inside $\Omega_{j}$
on the boundary $\Gamma_{j}$. 
If we revert back to the normal being defined as 
an outward normal to $\Omega_{j}$, then
the boundary conditions on $\Gamma_{j}$ 
is $\bt - i \eta \bu = 0$. 
From the uniqueness of solutions to the interior 
impedence problem, we conlcude that $\bu \equiv 0$
in $\Omega_{j}$, which in particular implies
that $2\bmu = \bu^{-}-\bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
$j=1,2,\ldots m$.
Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
invertible when $k^2$ is not a Dirichlet eigenvalue
for the Stokes equation on $\Omega$.

@@

The operator $-2\cD_{k} - 2\cW$ is trace class:
\begin{lemma}
  Suppose that $\Gamma$ is a $C^2$ curve.
  Then, $-2\cD_{k} - 2\cW \in \cJ_1(Y)$
  for all $k \in \mathbb{C} \setminus \{0\}$ 
\end{lemma}
\begin{proof}
Using Bessel function asymptotics, we note that the
kernel of $\cD_{k}$ given by $\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
has a leading order singularity of
$|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$ 
for all $k \in \mathbb{C} \setminus \{ 0\}$.
It follows from the criteria listed
in~\cite[Sec. 2]{bornemann2010numerical} that $\cD_{k}$
is a trace-class operator.
Since $\cW$ is a rank-one perturbation independent of $k$,
and trace-class operators are a vector space, we conclude
that $-2\cD_{k} - 2\cW$ is also a trace-class operator.
\end{proof}

>>>>

Before proving the main theorems, we require a number
of uniqueness results for oscillatory Stokes boundary
value problems.
%
To prove the uniqueness results, we follow the 
structure presented in Colton and Kress~\cite[Ch. 3]{colton1983integral}
for the scalar Helmholtz equation.
While uniqueness results for interior Dirichlet, Neumann, and impedance
problems follow from energy considerations and compactness
arguments, the proofs for uniqueness of exterior
results are more involved. 
In particular,
this entails making the exterior problems
well-posed by imposing an appropriate radiaiton condition.
We present well-posed boundary value formulations 
for both interior and exterior Dirichlet, Neumann and impedance
boundary value problems, and also
present uniqueness results for all of them.

@@

Let $\Omega$ be a bounded domain with $C^2$ boundary
denoted by $\Gamma$.
We summarize the interior Dirichlet, Neumann and impedance
boundary value problems in~\cref{def:int_dir,def:int_neu,def:int_imp} below.

\begin{definition}[Interior Dirichlet problem]
  \label{def:int_dir}
  Let $\ff \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:dir_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bu &= \ff \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}
Note that the divergence-free constraint for the oscillatory
Stokes equations implies a compatibility condition on the
Dirichlet data $\ff$, namely that
\begin{equation} \label{eq:dir_compat}
  \int_\Gamma \ff \cdot \bnu \, dS = 0 \; .
\end{equation}

\begin{definition}[Interior Neumann problem]
  \label{def:int_neu}
  Let $\bg \in C(\Omega)$ be given. Find $(\bu,p) \in A(\Omega)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt &= \bg \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

\begin{definition}[Interior impedance problem]
\label{def:int_imp}
  Let $\bh \in C(\Omega)$ be given and suppose 
  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)}>0$. 
  Find $(\bu,p) \in A(\Omega)$  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt - i \eta \bu &= \bh \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

@@

\begin{equation}
\left | \partial_{{\nu_x}} \left(\nabla^\perp \otimes
\nabla^\perp \left (H_0^{(1)} (kr) \right ) \right)\bpsi
- ik \left(\nabla^\perp \otimes \nabla^\perp
\left (H_0^{(1)} (kr) \right ) \right)\bpsi \right | =
o ( 1/\sqrt{r} ) \; . \nonumber
\end{equation}
Finally, since $H_0^{(1)}(kr)$ is radially symmetric,
we have

@@

Let $E$ and $\Gamma$ be as in the previous subsection.
The radiation condition allows for a well-posed formulation
of the exterior boundary value problems, which we
summarize in
\cref{def:dir_exterior,def:neu_exterior,def:imp_exterior} below.

@@

\begin{definition}[Exterior impedance problem]
  \label{def:imp_exterior}  
  Let $\bh \in C(\Gamma)$ be given and suppose that
  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)} >0$. 
  Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt + i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

@@

In the following lemma, we prove uniqueness for the
interior impedance problem.

@@

We now turn our attention to the proofs of the exterior boundary value problems
for the oscillatory Stokes equation. The following lemmas are useful for
proving these results.

@@

In the next lemma, we prove the analogue of Rellich's lemma for the
oscillatory Stokes equation. 
\begin{lem}
  \label{lem:rellich}
  Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose $k$ is real, $\bu$ satisfies the oscillatory
  Stokes equation in $E$, and that 
\begin{equation}
\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
\, . \label{eq:decayatinf}
\end{equation}
Then each component of $\bu$ is harmonic in $E$.
\end{lem}
\begin{proof}
We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
oscillatory biharmonic equation in $E$, i.e.
\begin{equation}
\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
\end{equation}
For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
j=1,2 \, . \nonumber
\end{equation}
Using Parseval's identity then
\begin{equation}
\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
|a_{2,n}(r)|^2 \, . \nonumber
\end{equation}
Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
\begin{equation}
\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
\end{equation}
Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
the functions $a_{j,n}$ are linear combinations of 
\begin{equation}
r^{|n|}, r^{-|n|}, H^{(1)}_{n}(k r), H^{(2)}_{n}(k r) \, , \quad
n\neq 0 \, , \nonumber
\end{equation}
and
\begin{equation}
1, \log{(r)}, H^{(1)}_{0}(k r), H^{(2)}_{0}(k r) \quad n=0 \, ,  \nonumber
\end{equation} 
where $H_{n}^{(1),(2)}(\cdot)$ are the Hankel functions of the first and
second kind of order $n$.
Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
expansion of $H_{n}^{(1),(2)}(kr)$ when $k$ and $r$ are real-valued, we note
that the projection of $a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$
must be zero. Thus, for sufficiently large $r$,
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
\, , \nonumber
\end{equation}
i.e. $u_{j}$ is harmonic 
in $B_{r}(0)^{c}$.
Finally, by \cref{cor:analytic}, $\bu$ is
analytic in $E$. Therefore, each $u_j$ is harmonic
throughout $E$.
\end{proof}

@@

\begin{remark}
  It should be noted that in~\cref{lem:rellich}, $\bu$ need
  not be a radiating solution. All that is assumed of $\bu$
  is that it satisfies the oscillatory Stokes equations in $E$.
\end{remark}

@@

The rank deficiency of $\cI-2\cDk$ is
well-known~\cite{biros2002embedded} and we summarize it
in the lemma below.

\begin{lem}
  \label{lem:nunull} In the notation above,
  $\bnu \in \cN(\cI - 2\cDkt)$.
\end{lem}
\begin{proof}
From~\cref{lem:propnullspacecorr}, we note that
$W[(\cI - 2\cD_{k})\bmu] =0$ implies that
$\left<(\cI -2\cD_{k})\bmu ,\bnu \right> = 0$ for
all $\bmu$, i.e. $\bnu \in R(\cI - 2\cD_{k})^{\perp}$, where
$R(A)$ denotes the range of the operator $A$. 
By the Fredholm alternative, the result then follows.
\end{proof}
Thus, we instead analyze the equation
\begin{equation}
(\cI - 2\cD_{k}  -2\cW) \bmu = -2\ff \; \, . \label{eq:inteq_dir_int_mod}
\end{equation}
Note that if $\ff$ satisfies the compatibility
condition $\int_\Gamma \ff \cdot \bnu \, dS =0$, then
\cref{eq:inteq_dir_int_mod} implies \cref{eq:inteq_dir_int}.

@@

\begin{thrm}
\label{thm:dlmain}
Suppose that $\Omega$ is a bounded, simply connected domain. Then, the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k^2$ is a
Dirichlet eigenvalue for the Stokes equation on $\Omega$.
\end{thrm}
\begin{proof}
  Suppose that $k^2$ is not a Dirichlet eigenvalue for
  the Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-}=(\cI - 2\cD_{k}) \bmu = 0$
on $\Gamma$. Since $k^2$ is not a Dirichlet eigenvalue for the Stokes
equation on $\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
In particular, this implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again, we conclude that the exterior limit
of the surface traction, $\bt^{+}$, is $0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Stokes equation in the exterior $E$, as $\cW[\bmu] = 0$ implies
$\int_{\Gamma} \bmu \cdot \bnu = 0$.
From the uniqueness of solutions to the exterior Neumann problem, 
we conclude that $\bu \equiv 0$ in $E$ as well,
which in particular implies that
the exterior limit of the velocity, $\bu^{+}$, is $0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $2\bmu = \bu^{-} - \bu^{+} = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k^2$
is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.

@@

\begin{thrm}
  Suppose that $\Omega$ is a multiply connected domain
  given by the intersection of a domain $\Omega_{0}$
  and the exterior of a single domain $\Omega_{1}$ with
  $ \bar\Omega_1 \subset \Omega_0$.
  Then, the operator $\cI - 2\cD_{k} - 2\cW$ is not invertible
  if $k^2$ is a Neumann eigenvalue of $\Omega_{1}$.
\end{thrm}

@@

\begin{proof}
  Suppose that $k^2$ is a Neumann eigenvalue of $\Omega_{1}$, and
  let $\tilde{\bu}$ denote the corresponding eigenfunction. 
  Note that $\tilde{\bu}$ is not identically $0$ on the boundary
  of $\Omega_{1}$, which we denote by $\Gamma_1$.
  Since $\tilde{\bu}$ is an interior Neumann eigenfunction, we note that
  the surface traction corresponding to the solution, $\bt^{-}$, is $0$
  on the boundary.
  Applying \cref{thrm:rep-theorem} to the
  solution $\tilde{\bu}$ in the interior
  and taking the interior limit we get
\begin{equation}
\tilde{\bu} = \frac{1}{2}\tilde{\bu} + \cD^{\Gamma_{1}}_{k}[\tilde{\bu}] +
\cS^{\Gamma_{1}} [\bt^{-}] \implies \frac{1}{2} \tilde{\bu} - \cD^{\Gamma_{1}}_{k}[\tilde{\bu}]
= 0\, .
\end{equation}
Note that the sign of the $\bD$ operator in the
representation theorem is switched since the normal
is pointing inwards for the boundary $\Omega_{1}$.
Thus, $\tilde{\bu}$ is a non-trivial null vector of the operator 
$\frac{1}{2}\cI - \cD^{\Gamma_{1}}_{k}$. 
Furthermore since $\tilde{\bu}$ is the boundary data of 
the solution of the oscillatory Stokes equation
in $\Omega_{1}$, we get that $\cW^{\Gamma_{1}}[\tilde{\bu}] = 0$.
Setting $\bmu = \tilde{\bu}$ on $\Gamma_{1}$, and
$\bmu = 0$ on $\Gamma_{0}$, we obtain a non-trivial null
vector for the operator $\cI - 2\cD^{\Gamma}_{k} -2\cW^{\Gamma}$
on the boundary $\Gamma = \Gamma_{0} \cup \Gamma_{1}$.
\end{proof}

The spurious eigenvalues of the operator $\cI-2\cDk-2\cW$
are demonstrated in \cref{subsec:spurannulus} on an annulus,
where both the true and spurious eigenvalues can be
determined analytically. 
Analogous with the observation in~\cite{zhao2015robust},
this lack of one-to-one correspondence between
the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
and the Dirichlet eigenvalues of the Stokes operator on multiply
connected domains also causes non-robustness and introduces near 
resonances for simply connected domains
which are almost multiply connected.

@@

The non-robustness in using the double layer
potential representation can be
remedied by using a combined-field, or mixed layer potential,
representation, i.e. setting $\bu = (\bD_{k} + i\eta \bS_{k})
\bmu$, with $\eta$ real and positive.
Imposing the Dirichlet boundary condition
and using~\cref{lem:jump-conds}, we obtain 
\begin{equation}
  (\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \,
  \textrm{ on } \Gamma. 
\end{equation}
As with the double layer representation, this
integral equation is rank deficient for any $k$.
Instead, we consider
\begin{equation}
(\cI - 2\cD_{k} -2i\eta \cS_{k}  -2\cW)\bmu = -2 \ff \, .
\end{equation}

@@

To show that $\bmu=0$ on
$\Gamma_{j}$, we observe that $\bu$ is also a
solution to the oscillatory Stokes equation in each
of the obstacles $\Omega_{j}$.
Using the jump conditions in~\cref{lem:jump-conds},
we get that $\bt^{+} = 2i\eta \bmu$ and $\bu^{+} = -2\bmu$.
However, the normal is inward pointing inside $\Omega_{j}$
on the boundary $\Gamma_{j}$. 
If we revert back to the normal being defined as 
an outward normal to $\Omega_{j}$, then
the boundary conditions on $\Gamma_{j}$ 
is $\bt - i \eta \bu = 0$. 
From the uniqueness of solutions to the interior 
impedance problem, we conlcude that $\bu \equiv 0$
in $\Omega_{j}$, which in particular implies
that $2\bmu = \bu^{-}-\bu^{+} = 0$ for $\xx \in \Gamma_{j}$,
$j=1,2,\ldots m$.
Thus, $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is
invertible when $k^2$ is not a Dirichlet eigenvalue
for the Stokes equation on $\Omega$.

@@

The operator $-2\cD_{k} - 2\cW$ is trace class:
\begin{lem}
  Suppose that $\Gamma$ is a $C^2$ curve.
  Then $-2\cD_{k} - 2\cW \in \cJ_1(Y)$
  for all $k \in \mathbb{C} \setminus \{0\}$ 
\end{lem}
\begin{proof}
Using Bessel function asymptotics, we note that the
kernel of $\cD_{k}$ given by $\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
has a leading order singularity of
$|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$ 
for all $k \in \mathbb{C} \setminus \{ 0\}$.
It follows from the criteria listed
in~\cite[Sec. 2]{bornemann2010numerical} that $\cD_{k}$
is a trace-class operator.
Since $\cW$ is a rank-one perturbation independent of $k$,
and trace-class operators are a vector space, we conclude
that $-2\cD_{k} - 2\cW$ is also a trace-class operator.
\end{proof}
